---
title: "Lab 00 - Hello IDS!"
author: "Yuchun Zhu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Yuchun Zhu", "Lim Zhen Yang", "Mingshi Yue", 
           "Kevin jiang", "Yifan Guo"),
  github_username = c("meessi15", "yangsubwayceo", "Ethanyue123", 
                      "jky040223", "Alen050426"), 
  colour = c("blue", "grey", "yellow", 
             "yellow", "green"),
  hobby = c("football", "listening to music", "woman", 
            "basketball", "playing chase"),
  favourite_number = c(10, 7, 6, 4, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


this code can create a bar chart with the data from the 'team_data'. Also, the code named the x-axis as github_username and the y-axis as favourite_number. Also the 'fill = colour' can define the colour of the bars in bar chart

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "eman", 
          y = "01 - 1 rebmun",
          title = "puorg")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
